Exploring the Motives and Driving Forces Behind Modifications to APIs From a Software Evolution Perspective

### 2015-05-06 thesis/paper.tex
table

                                   & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \Xhline{2\arrayrulewidth}
              Example Code         & U                         & R\textsubscript{f}        & R\textsubscript{f}        & U                  \\ \hline
              Documentation        & U                         & U                         & R\textsubscript{f}        & R\textsubscript{f} \\ \hline
              Interfaces           & G                         & P                         & P                         & G                  \\ \hline
              Error Handling       & P                         & P                         & G                         & G                  \\ \hline
              3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
              axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
              axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
              axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
              axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
              axevent              & E                         & E                         & G                         & G                  \\ \hline
              axhttp               & E                         & E                         & G                         & G                  \\ \hline
              ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
              Burst Mode           & R\textsubscript{d}        & R\textsubscript{d}        & N/A                       & N/A                \\

              \bottomrule
       \end{tabular}
       \caption{Category }
       \label{table:categories}
\end{table}

>>>>

                                   & \textbf{P}                & \textbf{A}                & \textbf{P}                & \textbf{A}         \\ \Xhline{2\arrayrulewidth}
              axptz                & E                         & E                         & N/A                       & N/A                \\ \hline
              axaudio              & E                         & E                         & N/A                       & N/A                \\ \hline
              axstorage            & E                         & E                         & N/A                       & N/A                \\ \hline
              axserialport         & E                         & E                         & N/A                       & N/A                \\ \hline
              axevent              & E                         & E                         & G                         & G                  \\ \hline
              axhttp               & E                         & E                         & G                         & G                  \\ \hline
              ax\_parameter        & E                         & E                         & G                         & G                  \\ \hline
              Burst Mode           & R\textsubscript{d}        & R\textsubscript{d}        & N/A                       & N/A                \\ \hline
              Example Code         & U                         & R\textsubscript{f}        & R\textsubscript{f}        & U                  \\ \hline
              Documentation        & U                         & U                         & R\textsubscript{f}        & R\textsubscript{f} \\ \hline
              Interfaces           & G                         & P                         & P                         & G                  \\ \hline
              3rd Party            & A                         & A                         & N/A                       & N/A                \\ \hline
              Error Handling       & P                         & P                         & G                         & G                  \\

              \bottomrule
       \end{tabular}
       \caption{Categorisation of Changes }
       \label{table:categories}
\end{table}
